A simplified dynamic bioenergetic model for coral-\emph{Symbiodinium} symbioses

### 2016-09-23 Rmd/JTB_ms.tex
add some text

To analyze qualitative behavior, we ran the model to steady state across
gradients of external irradiance and DIN, and plotted the specific
growth rate (Fig. 2A) and symbiont to host biomass ratio (Fig. 2B).
Results are consistent with observations in corals: specific growth
rates

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig2.png}
\caption{Steady state values of (A) specific growth
(\(Cmol \cdot Cmol^{-1} \cdot d^{-1}\)) and (B) the symbiont to host
biomass ratio (\(CmolS \cdot CmolH^{-1}\)) across gradients of external
irradiance and dissolved inorganic nitrogen. Simulations for each
combination of light and nutrients (21 points along each axis) were run
for 100 days with a time step of 1 day. Negative steady state growth
rates, and corresponding S:H ratios, were set to zero.}
\end{figure}

>>>>

To analyze qualitative behavior, we ran the model to steady state across
gradients of external irradiance and DIN, and plotted the specific
growth rate (Fig. 2A) and symbiont to host biomass ratio (Fig. 2B).
Results are consistent with observations in corals: specific growth
rates are low at very low levels of irradiance and DIN, as these
scenarios limit the availability of carbon and nitrogen, respectively,
to build biomass. As these resources increase, specific growth
increases, reaching its highest levels above 2 µM DIN and
\textasciitilde{}15 mol photons m\textsuperscript{-2}
d\textsuperscript{-1}.

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig2.png}
\caption{Steady state values of (A) specific growth (\$Cmol
Cmol\textsuperscript{-1} d\textsuperscript{-1}) and (B) the symbiont to
host biomass ratio (CmolS CmolH\textsuperscript{-1}) across gradients of
external irradiance and dissolved inorganic nitrogen. Simulations for
each combination of light and nutrients (21 points along each axis) were
run for 100 days with a time step of 1 day. Negative steady state growth
rates, and corresponding S:H ratios, were set to zero.}
\end{figure}
